The Three-HITs Theorem\footnote{This work was partially supported by COST Action CA15123.}

### 2017-03-21 Paper/Paper.tex
Fix affiliation, remove files that do not belong to git repo.
A git repository should contain *only source code*.
Label Definition 3.

%% Please provide for each author the \author and \affil macro, even when authors have the same affiliation, i.e. for each author there needs to be the  \author and \affil macros
\author[1]{Andrej Bauer}
\author[2]{Niels van der Weide}
\affil[1]{Department of Mathematics and Physics, University of Ljubljana, Ljubljana, Slovenia\\
  \texttt{Andrej.Bauer@andrej.com}}
\affil[2]{Department of Computer Science, Radboud University, Nijmegen, The Netherlands\\
  \texttt{nweide@cs.ru.nl}}
\authorrunning{A. Bauer and N. van der Weide} %mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et. al.'

@@

\newcommand{\Boperator}[1]{\mathrm{\mathbf{#1}}}
\newcommand{\comment}[1]{-- #1 --}
\newcommand{\remove}[1]{}
\newcommand{\inn}{\Boperator{in}}

@@

\section{Introduction}
Higher inductive types (HITs) generalize normal inductive types by allowing constructors for both points and paths, rather than just for the points.
While an inductive type is freely generated from a signature, a higher inductive type is freely generated from a signature with some equations.
Numerous examples and definitions of such types have already been given in the literature \cite{altenkirch2016quotient,awodey2012inductive,basoldhigher,sojakova2015higher,hottbook}, but a definition with a good metatheory is still lacking.
As a step towards that goal, we simplify the definition given in \cite{basoldhigher} bringing it closer to the intuition and the intended meaning.

@@

Next we define the notion of a constructor term.
\begin{definition}
Given is a function $c : A \> T \rightarrow T$.
Then we say $t$ is a \emph{constructor term} over $c$ if we can find polynomials $F$ and $G$ such that $x : F \> T \Vdash t : G \> T$ can be derived using the following rules.
\begin{gather*}
	\AxiomC{$t : B$}
	\AxiomC{$T$ does not occur in $B$}
	\BinaryInfC{$x:F \> T \Vdash t : B$}
	\bottomAlignProof
	\DisplayProof 
	 \quad
	\AxiomC{}
	\UnaryInfC{$x : F \> T \Vdash x : F \> T$}
	\bottomAlignProof
	\DisplayProof
	\quad
	\AxiomC{$x : F \> T \Vdash r : A \> T$}
	\UnaryInfC{$x : F \> T \Vdash c \> r : T$}
	\bottomAlignProof
	\DisplayProof
	\\[7pt]
	\AxiomC{$j \in \{1, 2\}$}
	\AxiomC{$x : F \> T \Vdash r : G_1 \> T \times G_2 \> T$}
	\BinaryInfC{$x : F \> T \Vdash\pi_j \> r : G_j \> T$}
	\bottomAlignProof
	\DisplayProof
	\quad
	\AxiomC{$j \in \{1, 2\}$}
	\AxiomC{$x : F \> T \Vdash r_j : G_j$}
	\BinaryInfC{$x : F \> T \Vdash (r_1, r_2) : G_1 \> T\times G_2 \> T$}
	\bottomAlignProof
	\DisplayProof
	\\[7pt]
	\AxiomC{$j \in \{1, 2\}$}
	\AxiomC{$x : F \> T \Vdash r : G_j \> T$}
	\BinaryInfC{$x : F \> T : \inn_j \> r : G_1 \> T + G_2 \> T$}
	\bottomAlignProof
	\DisplayProof
\end{gather*}
\end{definition}

@@

\bibliography{lipics-v2016-sample-article}

>>>>

%% Please provide for each author the \author and \affil macro, even when authors have the same affiliation, i.e. for each author there needs to be the  \author and \affil macros
\author[1]{Andrej Bauer}
\author[2]{Niels van der Weide}
\affil[1]{Faculty of Mathematics and Physics, University of Ljubljana, Ljubljana, Slovenia\\
  \texttt{Andrej.Bauer@andrej.com}}
\affil[2]{Department of Computer Science, Radboud University, Nijmegen, The Netherlands\\
  \texttt{nweide@cs.ru.nl}}
\authorrunning{A.\ Bauer and N.\ van der Weide} %mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et. al.'

@@

\newcommand{\Boperator}[1]{\mathsf{#1}}
\newcommand{\comment}[1]{-- #1 --}
\newcommand{\remove}[1]{}
\newcommand{\inn}{\Boperator{in}}

@@

\section{Introduction}
Higher inductive types (HITs) generalize normal inductive types by allowing constructors for both points and paths, rather than just for the points.
While an inductive type is freely generated from a signature, a higher inductive type is freely generated from a signature together with constructors for equations.
Numerous examples and definitions of such types have already been given in the literature \cite{altenkirch2016quotient,awodey2012inductive,basoldhigher,sojakova2015higher,hottbook}, but a definition with a good metatheory is still lacking.
As a step towards that goal, we simplify the definition given in \cite{basoldhigher} bringing it closer to the intuition and the intended meaning.

@@

Next we define the notion of a constructor term.
\begin{definition}
\label{def:constructor-term}
Given is a function $c : A \> T \rightarrow T$.
Then we say $t$ is a \emph{constructor term} over $c$ if we can find polynomials $F$ and $G$ such that $x : F \> T \Vdash t : G \> T$ can be derived using the following rules.
\begin{gather*}
        \AxiomC{$t : B$}
        \AxiomC{$T$ does not occur in $B$}
        \BinaryInfC{$x:F \> T \Vdash t : B$}
        \bottomAlignProof
        \DisplayProof 
         \quad
        \AxiomC{}
        \UnaryInfC{$x : F \> T \Vdash x : F \> T$}
        \bottomAlignProof
        \DisplayProof
        \quad
        \AxiomC{$x : F \> T \Vdash r : A \> T$}
        \UnaryInfC{$x : F \> T \Vdash c \> r : T$}
        \bottomAlignProof
        \DisplayProof
        \\[7pt]
        \AxiomC{$j \in \{1, 2\}$}
        \AxiomC{$x : F \> T \Vdash r : G_1 \> T \times G_2 \> T$}
        \BinaryInfC{$x : F \> T \Vdash\pi_j \> r : G_j \> T$}
        \bottomAlignProof
        \DisplayProof
        \quad
        \AxiomC{$j \in \{1, 2\}$}
        \AxiomC{$x : F \> T \Vdash r_j : G_j$}
        \BinaryInfC{$x : F \> T \Vdash (r_1, r_2) : G_1 \> T\times G_2 \> T$}
        \bottomAlignProof
        \DisplayProof
        \\[7pt]
        \AxiomC{$j \in \{1, 2\}$}
        \AxiomC{$x : F \> T \Vdash r : G_j \> T$}
        \BinaryInfC{$x : F \> T : \inn_j \> r : G_1 \> T + G_2 \> T$}
        \bottomAlignProof
        \DisplayProof
\end{gather*}
\end{definition}

@@

\bibliography{Paper}
